Modern BTree\\ techniques

### 2019-12-23 btree/presentation.tex
Base for btree

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage[normalem]{ulem}

@@

\usetikzlibrary{shapes,arrows,positioning,shadows.blur,shapes.geometric,fit, calc, backgrounds, decorations.pathmorphing, shapes.geometric, decorations.pathreplacing, arrows.meta}

\graphicspath{{images/}}
\newfontfamily{\FA}{FontAwesome}

\definecolor{check}{rgb}{0.1,2,0.3}
\definecolor{fail}{rgb}{2,0.1,0.1}
\definecolor{question}{rgb}{0.9,0.9,0.0}

\def\twitter{{\FA \faTwitter}}
\def\github{{\FA \faGithub}}
\def\email{{\FA \faEnvelope}}
\def\spin{{\FA \faSpinner}}
\def\check{\textcolor{check}{\FA \faCheck}}
\def\fail{\textcolor{fail}{\FA \faRemove}}
\def\question{\textcolor{question}{\FA \faSearch}}

@@

\definecolor{links}{HTML}{0099FF}
\hypersetup{colorlinks, linkcolor=, urlcolor=links}

@@

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 03-10-2019}%

@@

\title{K8S RESOURCE\\ SHARING}
\subtitle{FOR POSTGRESQL\\ EXPERTS}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

@@

\begin{frame}
    \frametitle{}
    \begin{minipage}{14cm}
        \begin{center}

        \vspace{10mm}
        \includegraphics[width=1.0\textwidth,center]{acid_team.png}

        \vspace{5mm}

        \href{https://github.com/zalando/patroni}
             {\color{black}\normalsize{patroni}} \&
        \href{https://github.com/zalando-incubator/postgres-operator}
             {\color{black}\normalsize{postgres-operator}}
        \end{center}
    \end{minipage}
\end{frame}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}
        resources:
          requests:
            cpu: "1000m"
            memory: "1GB"
          limits:
            cpu: "2000m"
            memory: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \vspace*{-2.5em}
            \begin{center}
            \fontsize{88pt}{90}\selectfont{\color{black} \textbf{?}}
            \end{center}
        \end{column}

    \end{columns}
\end{frame}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Allocatable}

        \begin{onlyenv}<1>
            \begin{minted}[fontsize=\normalsize,escapeinside=??]{bash}
            Capacity:
             cpu:                         16
             hugepages-1Gi:               0
             hugepages-2Mi:               0
             memory:                      65947396Ki
            Allocatable:
             cpu:                         15800m
             hugepages-1Gi:               0
             hugepages-2Mi:               0
             memory:                      65388292Ki
            \end{minted}

            \vspace{-6.0cm}
            \begin{tikzpicture}
                \draw[
                    transparent=1.0,
                    color=red,
                    line width=1.5mm,
                    rotate=10,
                    pattern=north west lines,
                    pattern color=red!30
                ] (0, 0) ellipse (4cm and 2cm) node[pos=0.0] {
                    \fontsize{28pt}{28}\selectfont
                    {\textbf{K8S appliance?}
                    }};
            \end{tikzpicture}
        \end{onlyenv}

        \begin{onlyenv}<2>
            \color{gray}
            \begin{minted}[fontsize=\normalsize,escapeinside=??]{bash}
            Capacity:
             cpu:                         16
             hugepages-1Gi:               0
             hugepages-2Mi:               0
             memory:                      65947396Ki
            Allocatable:
             cpu:                         15800m
             hugepages-1Gi:               0
             hugepages-2Mi:               0
             memory:                      65388292Ki
            \end{minted}

            \vspace{-6.0cm}
            \begin{tikzpicture}
                \draw[
                    color=red,
                    line width=1.5mm,
                    rotate=10,
                    pattern=north west lines,
                    pattern color=red!30
                ] (0, 0) ellipse (4cm and 2cm) node[pos=0.0] {
                    \fontsize{28pt}{28}\selectfont
                    {\textbf{K8S appliance?}
                    }};
            \end{tikzpicture}
        \end{onlyenv}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
        \vspace{1.0cm}

        \only<1>{
        \begin{tikzpicture}[component/.style={
                regular polygon,
                regular polygon sides=4,
                rounded corners,
                line width=0.5mm,
        }]
            \draw[component, color=white] (0, 0) rectangle (2.8, 2.8) node[pos=0.5] {\textbf{cgroups}};
            \draw[component, color=white] (3.2, 3.2) rectangle (6.0, 6.0) node[pos=0.5] {\textbf{caps}};
            \draw[component, color=white] (0, 3.2) rectangle (2.8, 6.0) node[pos=0.5] {\textbf{ns}};
            \draw[component, color=white] (3.2, 0) rectangle (6.0, 2.8) node[pos=0.5] {\textbf{root}};
        \end{tikzpicture}
        }

        \only<2>{
        \begin{tikzpicture}[component/.style={
                regular polygon,
                regular polygon sides=4,
                rounded corners,
                line width=0.5mm,
        }]
            \draw[component, fill=blue!20] (0, 0) rectangle (2.8, 2.8) node[pos=0.5] {\textbf{cgroups}};
            \draw[component, color=white] (3.2, 3.2) rectangle (6.0, 6.0) node[pos=0.5] {\textbf{caps}};
            \draw[component, color=white] (0, 3.2) rectangle (2.8, 6.0) node[pos=0.5] {\textbf{ns}};
            \draw[component, color=white] (3.2, 0) rectangle (6.0, 2.8) node[pos=0.5] {\textbf{root}};
        \end{tikzpicture}
        }

        \only<3>{
        \begin{tikzpicture}[component/.style={
                regular polygon,
                regular polygon sides=4,
                rounded corners,
                line width=0.5mm,
        }]
            \draw[component, fill=blue!20] (0, 0) rectangle (2.8, 2.8) node[pos=0.5] {\textbf{cgroups}};
            \draw[component, color=white] (3.2, 3.2) rectangle (6.0, 6.0) node[pos=0.5] {\textbf{caps}};
            \draw[component, fill=red!20] (0, 3.2) rectangle (2.8, 6.0) node[pos=0.5] {\textbf{ns}};
            \draw[component, color=white] (3.2, 0) rectangle (6.0, 2.8) node[pos=0.5] {\textbf{root}};
        \end{tikzpicture}
        }

        \only<4>{
        \begin{tikzpicture}[component/.style={
                regular polygon,
                regular polygon sides=4,
                rounded corners,
                line width=0.5mm,
        }]
            \draw[component, fill=blue!20] (0, 0) rectangle (2.8, 2.8) node[pos=0.5] {\textbf{cgroups}};
            \draw[component, fill=green!20] (3.2, 3.2) rectangle (6.0, 6.0) node[pos=0.5] {\textbf{caps}};
            \draw[component, fill=red!20] (0, 3.2) rectangle (2.8, 6.0) node[pos=0.5] {\textbf{ns}};
            \draw[component, color=white] (3.2, 0) rectangle (6.0, 2.8) node[pos=0.5] {\textbf{root}};
        \end{tikzpicture}
        }

        \only<5>{
        \begin{tikzpicture}[component/.style={
                regular polygon,
                regular polygon sides=4,
                rounded corners,
                line width=0.5mm,
        }]
            \draw[component, fill=blue!20] (0, 0) rectangle (2.8, 2.8) node[pos=0.5] {\textbf{cgroups}};
            \draw[component, fill=green!20] (3.2, 3.2) rectangle (6.0, 6.0) node[pos=0.5] {\textbf{caps}};
            \draw[component, fill=red!20] (0, 3.2) rectangle (2.8, 6.0) node[pos=0.5] {\textbf{ns}};
            \draw[component, fill=yellow!20] (3.2, 0) rectangle (6.0, 2.8) node[pos=0.5] {\textbf{root}};
        \end{tikzpicture}
        }

        \href{https://github.com/opencontainers/runc/blob/master/libcontainer/SPEC.md}
        {\color{black}\normalsize{libcontainer/SPEC.md}}
    \end{center}
\end{frame}
\note{
    root is about chroot/pivot_root
}

@@

    \only<1>{
        \begin{center}
        \begin{tikzpicture}[]

        \def\firstcircle{(0,0) circle (1.5cm)}
        \def\secondcircle{(60:4cm) circle (1.5cm)}
        \def\thirdcircle{(0:4cm) circle (1.5cm)}

        \begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5, line width=0.5mm]
            \fill[red] \firstcircle;
            \fill[green] \secondcircle;
            \fill[blue] \thirdcircle;

            \draw \firstcircle node [] {\textbf{res}};
            \draw \secondcircle node [] {\textbf{limit}};
            \draw \thirdcircle node [] {\textbf{time}};
        \end{scope}
        \end{tikzpicture}
        \end{center}
    }

    \only<2> {
        \begin{center}
        \begin{tikzpicture}[]

        \def\firstcircle{(0,0) circle (1.5cm)}
        \def\secondcircle{(60:2cm) circle (1.5cm)}
        \def\thirdcircle{(0:2cm) circle (1.5cm)}

        \begin{scope}[shift={(3cm,-5cm)}, fill opacity=0.5, line width=0.5mm]
            \fill[red] \firstcircle;
            \fill[green] \secondcircle;
            \fill[blue] \thirdcircle;

            \draw \firstcircle node [below] {\textbf{res}};
            \draw \secondcircle node [above] {\textbf{limit}};
            \draw \thirdcircle node [below] {\textbf{time}};
        \end{scope}
        \end{tikzpicture}
        \end{center}
    }

\begin{frame}
    \frametitle{}
    \begin{columns}

        \begin{column}{0.15\columnwidth}
        \end{column}

        \begin{column}{0.35\columnwidth}
        \begin{itemize}[label={\MVRightarrow}]
            \item docker
            \item rkt
            \item LXC
            \item $\cdots$
        \end{itemize}
        \end{column}

        \begin{column}{0.48\columnwidth}
        \begin{itemize}[label={\MVRightarrow}]
            \item podman
            \item cgroup v1
            \item cgroup v2
            \item $\cdots$
        \end{itemize}
        \end{column}

    \end{columns}

@@

    \begin{tikzpicture}[
        scale=0.6,
        every node/.style={draw=black!70,fill=red!30,rounded corners,thick,anchor=west, minimum width=4cm,transform shape, blur shadow={shadow blur steps=5,shadow blur extra rounding=1.3pt}, inner sep=.5cm},
        inactive/.style={fill=gray!30},
        to/.style={->,>=stealth',shorten >=1pt,semithick,font=\sffamily\footnotesize},
        ]
      \node [fill=yellow!20] (cgroup-v1) {cgroup v1};
      \node [below=.5cm of cgroup-v1] (cpu) {CPU};
      \node [inactive, left=.5cm of cpu] (systemd) {Systemd};
      \node [inactive, right=.5cm of cpu] (memory) {Memory};
      \node [inactive, right=.5cm of memory, minimum width=1cm, inner sep=0.7cm] (rest) {\ldots};
      \node [below=.5cm of cpu] (k8s) {K8S};
      \node [below=.5cm of k8s] (guaranteed) {Guaranteed};
      \node [inactive, right=.5cm of guaranteed] (burstable) {Burstable};
      \node [inactive, left=.5cm of guaranteed] (bestefforts) {Best Efforts};
      \node [below=.5cm of guaranteed] (pause) {Pause};
      \node [below=.5cm of pause] (app) {App};

      \draw[to] (cgroup-v1) -- (cpu);
      \draw[to] (cgroup-v1) -| (memory);
      \draw[to] (cgroup-v1) -| (rest);
      \draw[to] (cgroup-v1) -| (systemd);
      \draw[to] (cpu) -- (k8s);
      \draw[to] (k8s) -- (guaranteed);
      \draw[to] (k8s) -| (bestefforts);
      \draw[to] (k8s) -| (burstable);
      \draw[to] (guaranteed) -- (pause);
      \draw[to] (pause) -- (app);
    \end{tikzpicture}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}

    \begin{columns}
    \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize,escapeinside=??]{yaml}
        resources:
          requests:
            cpu: "1000m" ?\tikzmark{cpu_req}?
            memory: "1GB"
          limits:
            cpu: "2000m" ?\tikzmark{cpu_lim}?
            memory: "2GB"
        \end{minted}
    \end{column}

    \begin{column}{0.48\columnwidth}
        \begin{tikzpicture}[remember picture,
            every node/.style={
                fill=red!30,
                rounded corners=0.2cm,
                minimum width=3cm,
                inner sep=0.5cm,
            },
            baseline=(cpu_req.south), anchor=base
            ]
          \draw node[] (cpu_shares) {\textbf{cpu share}};
          \draw node[below=0.3 of cpu_shares] (cpu_cfs) {\textbf{cfs quota}};

          \draw [overlay, ->, line width=3pt, red] (cpu_req) -- (cpu_shares.west);
          \draw [overlay, ->, line width=3pt, red] (cpu_lim) -- (cpu_cfs.west);
        \end{tikzpicture}
    \end{column}
    \end{columns}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Share}

        \vspace{1.0cm}
        \only<1>{
            \begin{tikzpicture}
                \draw[
                    line width=0.5mm,
                    fill=red!30
                ] (0.0,0.0) rectangle (4.0,2.0) node[pos=.5] {\textbf{C1}};

                \draw[
                    line width=0.5mm,
                    fill=blue!30
                ] (4.0,0.0) rectangle (8.0,2.0) node[pos=.5] {\textbf{C2}};

            \end{tikzpicture}
        }

        \only<2>{
            \begin{tikzpicture}

                \draw[
                    line width=0.5mm,
                    fill=red!30
                ] (0.0,0.0) rectangle (2.0,2.0) node[pos=.5] {\textbf{C1}};

                \draw[
                    line width=0.5mm,
                    fill=blue!30
                ] (2.0,0.0) rectangle (4.0,2.0) node[pos=.5] {\textbf{C2}};

                \draw[
                    line width=0.5mm,
                    fill=green!30
                ] (4.0,0.0) rectangle (6.0,2.0) node[pos=.5] {\textbf{C3}};

                \draw[
                    line width=0.5mm,
                    fill=gray!30
                ] (6.0,0.0) rectangle (8.0,2.0) node[pos=.5] {\textbf{C4}};

            \end{tikzpicture}
        }

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Quota}

        \vspace{1.0cm}
        \only<1>{
            \begin{tikzpicture}
                \draw[
                    line width=0.5mm,
                    fill=red!30
                ] (0.0,0.0) rectangle (2.0,2.0) node[pos=.5] {\textbf{C1}};

                \draw[
                    line width=0.5mm,
                    fill=blue!30
                ] (2.0,0.0) rectangle (4.0,2.0) node[pos=.5] {\textbf{C2}};

                \draw[
                    line width=0.5mm,
                    dashed
                ] (4.0,0.0) rectangle (8.0,2.0) node[pos=.5] {};

            \end{tikzpicture}
        }

        \only<2>{
            \begin{tikzpicture}

                \draw[
                    line width=0.5mm,
                    fill=red!30
                ] (0.0,0.0) rectangle (2.0,2.0) node[pos=.5] {\textbf{C1}};

                \draw[
                    line width=0.5mm,
                    fill=blue!30
                ] (2.0,0.0) rectangle (4.0,2.0) node[pos=.5] {\textbf{C2}};

                \draw[
                    line width=0.5mm,
                    fill=green!30
                ] (4.0,0.0) rectangle (6.0,2.0) node[pos=.5] {\textbf{C3}};

                \draw[
                    line width=0.5mm,
                    fill=gray!30
                ] (6.0,0.0) rectangle (8.0,2.0) node[pos=.5] {\textbf{C4}};

            \end{tikzpicture}
        }

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Bandwidth accounting}

        \begin{flushleft}
        \begin{minted}[fontsize=\LARGE]{bash}
# from /proc/sys/kernel/
sched_cfs_bandwidth_slice_us
# default=5ms
        \end{minted}
        \end{flushleft}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Exclusive CPU}

        \begin{itemize}[label={\MVRightarrow}]
            \item cpu management policy
            \item kube-reserved
			\item guaranteed (integer quantity)
            \item cpuset.cpus
            \item cpuset.cpuset.cpu\_exclusive
        \end{itemize}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}

    \begin{overprint}
    \onslide<1>
        \begin{columns}
        \begin{column}{0.48\columnwidth}
            \begin{minted}[fontsize=\normalsize,escapeinside=??]{yaml}
            resources:
              requests:
                cpu: "1000m"
                memory: "1GB" ?\tikzmark{mem_req}?
              limits:
                cpu: "2000m"
                memory: "2GB" ?\tikzmark{mem_lim}?
            \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \begin{tikzpicture}[remember picture,
                every node/.style={
                    fill=red!30,
                    rounded corners=0.2cm,
                    minimum width=3cm,
                    inner sep=0.5cm,
                },
                baseline=(mem_req.south), anchor=base
                ]
              \draw node[] (soft_mem) {\textbf{soft mem limit}};
              \draw node[below=0.3 of soft_mem] (hard_mem) {\textbf{hard mem limit}};

              \draw [overlay, ->, line width=3pt, red] (mem_req) -- (soft_mem.west);
              \draw [overlay, ->, line width=3pt, red] (mem_lim) -- (hard_mem.west);

              \draw[
                  -,
                  line width=1.75mm,
                  color=red,
                  transparent=1.0,
              ] (soft_mem.south west) to (soft_mem.north east);

              \draw[
                  -,
                  line width=1.75mm,
                  color=red,
                  transparent=1.0,
              ] (soft_mem.south east) to (soft_mem.north west);

            \end{tikzpicture}
        \end{column}
        \end{columns}

    \onslide<2>
        \begin{columns}
        \begin{column}{0.48\columnwidth}
            \begin{minted}[fontsize=\normalsize,escapeinside=??]{yaml}
            resources:
              requests:
                cpu: "1000m"
                memory: "1GB" ?\tikzmark{mem_req}?
              limits:
                cpu: "2000m"
                memory: "2GB" ?\tikzmark{mem_lim}?
            \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \begin{tikzpicture}[remember picture,
                every node/.style={
                    fill=red!30,
                    rounded corners=0.2cm,
                    minimum width=3cm,
                    inner sep=0.5cm,
                },
                baseline=(mem_req.south), anchor=base
                ]
              \draw node[] (soft_mem) {\textbf{soft mem limit}};
              \draw node[below=0.3 of soft_mem] (hard_mem) {\textbf{hard mem limit}};

              \draw [overlay, ->, line width=3pt, red, transparent=1.0] (mem_req) -- (soft_mem.west);
              \draw [overlay, ->, line width=3pt, red] (mem_lim) -- (hard_mem.west);

              \draw[
                  -,
                  line width=1.75mm,
                  color=red,
              ] (soft_mem.south west) to (soft_mem.north east);

              \draw[
                  -,
                  line width=1.75mm,
                  color=red,
              ] (soft_mem.south east) to (soft_mem.north west);
            \end{tikzpicture}
        \end{column}
        \end{columns}
\end{overprint}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Memory reclaim}

        \begin{flushleft}
        \begin{minted}[fontsize=\normalsize]{bash}
# only under the memory pressure
=> page_reclaim.py --container 89c33bb3133f

[7382] postgres: 928K
[7138] postgres: 152K
[7136] postgres: 180K
[7468] postgres: 72M
[7464] postgres: 57M
[5451] postgres: 1M
        \end{minted}
        \end{flushleft}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Memory}

        \begin{itemize}[label={\MVRightarrow}]
            \item best efforts
            \item requests for QoS and oom\_adj
            \item memory.kmem.limit\_in\_bytes
            \item MEMCG\_CHARGE\_BATCH (32 pages)
            \item shared memory CoW
        \end{itemize}

    \end{center}
\end{frame}
\note{
    kmem limit attributed as part of mem limit
}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}
    resources:
      requests:
        cpu: "1000m"
        memory: "1GB"
        hugepages-1Gi: "1GB"
        hugepages-2Mi: "1GB"
      limits:
        cpu: "2000m"
        memory: "2GB"
        hugepages-1Gi: "2GB"
        hugepages-2Mi: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \vspace*{-2.5em}
            \begin{center}
                \begin{itemize}
                    \item <+->
                \end{itemize}

                \begin{itemize}[label={\MVRightarrow}]
                    \item classic
                    \item \sout{transparent}
                    \item isolation only per pod
                    \item no soft limits or reclaim (SIGBUS)
                \end{itemize}
            \end{center}
        \end{column}

    \end{columns}
\end{frame}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Huge pages experiment}

    \begin{overprint}
        \onslide<1>
        \begin{flushleft}
        \begin{minted}[fontsize=\normalsize,escapeinside=||]{python}
# perf record -e dTLB-loads,dTLB-stores -p PID
# huge_pages on
Samples: 832K of event 'dTLB-load-misses'
Event count (approx.): 640614445 : |\colorbox{White}{\textbf{~19%}}| less
Samples: 736K of event 'dTLB-store-misses'
Event count (approx.): 72447300 : |\colorbox{White}{\textbf{~29%}}| less

# huge_pages off
Samples: 894K of event 'dTLB-load-misses'
Event count (approx.): 784439650
Samples: 822K of event 'dTLB-store-misses'
Event count (approx.): 101471557
        \end{minted}
        \end{flushleft}

        \onslide<2>
        \begin{flushleft}
        \begin{minted}[fontsize=\normalsize,escapeinside=||]{python}
# perf record -e dTLB-loads,dTLB-stores -p PID
# huge_pages on
Samples: 832K of event 'dTLB-load-misses'
Event count (approx.): 640614445 : |\colorbox{RedOrange}{\textbf{~19%}}| less
Samples: 736K of event 'dTLB-store-misses'
Event count (approx.): 72447300 : |\colorbox{RedOrange}{\textbf{~29%}}| less

# huge_pages off
Samples: 894K of event 'dTLB-load-misses'
Event count (approx.): 784439650
Samples: 822K of event 'dTLB-store-misses'
Event count (approx.): 101471557
        \end{minted}
        \end{flushleft}

    \end{overprint}
    \end{center}
\end{frame}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}

    resources:
      requests:
        cpu: "1000m"
        memory: "1GB"
        hugepages-1Gi: "1GB"
        hugepages-2Mi: "1GB"
      limits:
        cpu: "2000m"
        memory: "2GB"
        hugepages-1Gi: "2GB"
        hugepages-2Mi: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \vspace*{-2.5em}
            \begin{center}
            \fontsize{28pt}{30}\selectfont{\color{black} \textbf{What is missing?}}
            \end{center}
        \end{column}

    \end{columns}
\end{frame}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}

    resources:
      requests:
        cpu: "1000m"
        memory: "1GB"
        hugepages-1Gi: "1GB"
        hugepages-2Mi: "1GB"
      limits:
        cpu: "2000m"
        memory: "2GB"
        hugepages-1Gi: "2GB"
        hugepages-2Mi: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \begin{center}
            \begin{minted}[fontsize=\normalsize]{yaml}
resources:
  requests:
    io: "?"
    llcache: "?"
    network: "?"

  limits:
    io: "?"
    llcache: "?"
    network: "?"

            \end{minted}
            \end{center}
        \end{column}

    \end{columns}
\end{frame}

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{LLCache}

        %\begin{flushleft}
		%\begin{minted}[fontsize=\normalsize]{bash}
%=> pqos -s
%L3CA COS definitions for Socket 0:
	%L3CA COS0 => MASK 0xffff
	%L3CA COS1 => MASK 0xf
	%L3CA COS2 => MASK 0xff0
	%L3CA COS3 => MASK 0xfff
%Core information for socket 0:
	%Core 0, L2ID 0, L3ID 0 => COS0
	%Core 1, L2ID 1, L3ID 0 => COS0
	%Core 2, L2ID 0, L3ID 0 => COS0
	%Core 3, L2ID 1, L3ID 0 => COS0
        %\end{minted}
        %\end{flushleft}

    %\end{center}
%\end{frame}

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{LLCache}

        %\begin{flushleft}
		%\begin{minted}[fontsize=\normalsize]{bash}
%# COS1 4 cache ways, COS 2 next 8 cache ways
%=> pqos -e "llc:1=0x000f;llc:2=0x0ff0;"
%SOCKET 0 L3CA COS1 => MASK 0xf
%SOCKET 0 L3CA COS2 => MASK 0xff0
%Allocation configuration altered.
        %\end{minted}
        %\end{flushleft}

    %\end{center}
%\end{frame}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Block I/O}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}

@@

\usetikzlibrary{shapes,arrows,positioning}
\graphicspath{{images/}}
\newfontfamily{\FA}{FontAwesome}

\def\twitter{{\FA \faTwitter}}
\def\github{{\FA \faGithub}}
\def\email{{\FA \faEnvelope}}

@@

\definecolor{links}{HTML}{0099FF}
\hypersetup{colorlinks, linkcolor=, urlcolor=links}
\definecolor{greenGood}{HTML}{99FF99}
\definecolor{redBad}{HTML}{FF9980}

@@

    \vspace*{1.5em}
    \fontsize{8pt}{10}\selectfont
    {\color{black} 03-12-2019}%

@@

\title{Modern BTree\\ techniques}
\subtitle{}
\date{\today}
\author{DMITRY DOLGOV}
\institute{}

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \only<1>{
            \includegraphics[width=0.5\textwidth,center]{tree.jpg}
            \vspace{-0.8cm}
            \hspace*{6cm}
            \href{https://www.flickr.com/photos/aspis7/5075169756/}
                 {\color{white}\fontsize{5pt}{0}\selectfont @aspis7}
        }
        \only<2>{
            \includegraphics[width=0.5\textwidth,center]{cs_tree.jpg}
            \vspace{-0.8cm}
            \hspace*{6cm}
            \href{https://www.flickr.com/photos/aspis7/5075169756/}
                 {\color{white}\fontsize{5pt}{0}\selectfont @aspis7}
        }
    \end{center}
\end{frame}

@@

    \begin{itemize}[label={\MVRightarrow}]
        \item <+-> Graefe, Goetz and Harumi A. Kuno. “Modern B-tree
            techniques.” IEEE 27th International Conference on Data
            Engineering, 2011.
        \item <+-> D. Comet, "Ubiquitous B-tree", ACM Comp. Surv., vol. 11, no.
            2, 1979.
    \end{itemize}
\end{frame}

    \def\arraystretch{1.5}
    \begin{tabular}{cccc}
        B-Tree & B$^{+}$-Tree & B$_{link}$-Tree & DP-Tree \\
        wB$^{+}$-Tree & NV-Tree & FP-Tree & FASTFAIR \\
        HiKV & Mass-Tree & Skip List & ART \\
        WORT & CDDS-Tree & Bw-Tree & HOT \\
        KISS-Tree & VAST-Tree & FAST & HV-Tree \\
        UB-Tree & LHAM & MDM & Hybrid B$^{+}$-Tree
    \end{tabular}
\end{frame}

@@

    \only<1>
    {
        \begin{tikzpicture}[]
            \node [rum-node] (memory) at ( 3, 0) {Mem};
            \node [rum-node] (write) at (-3, 0) {Write};
            \node [rum-node] (read) at ( 0, 3) {Read};
            \draw (read) -- (write) -- (memory) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (write.center) --
                    (memory.center) -- cycle;
            \end{scope}
        \end{tikzpicture}
    }

    \only<2>
    {
        \begin{tikzpicture}[]
            \node [rum-node, fill=greenGood] (memory) at ( 3, 0) {Mem};
            \node [rum-node, fill=redBad] (write) at (-3, 0) {Write};
            \node [rum-node, fill=greenGood] (read) at ( 0, 3) {Read};
            \draw (read) -- (write) -- (memory) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (write.center) --
                    (memory.center) -- cycle;
            \end{scope}
        \end{tikzpicture}
    }

    \only<3>
    {
        \begin{tikzpicture}[]
            \node [rum-extra-node] (complex) at ( 0, -3) {Complexity?};
            \node [rum-node] (memory) at ( 3, 0) {Mem};
            \node [rum-node] (write) at (-3, 0) {Write};
            \node [rum-node] (read) at ( 0, 3) {Read};
            \draw (read) -- (memory) -- (complex) -- (write) -- (read);
            \begin{scope}[on background layer]
                \fill [gray, opacity=0.2]
                    (read.center) --
                    (memory.center) --
                    (complex.center) --
                    (write.center) -- cycle;
            \end{scope}
        \end{tikzpicture}
    }

@@

    \begin{tikzpicture}[]
        \path
          node[minimum height=1cm, draw] (pointer1) {}
          node[minimum height=1cm, pattern=north west lines, draw, right=0 of pointer1] (sep1) {}
          node[minimum height=1cm, pattern=north west lines, draw, left=0 of pointer1] (sep2) {}
          node[minimum height=1cm, draw, right=0 of sep1] (pointer2) {}
          node[minimum height=1cm, draw, left=0 of sep2] (pointer3) {}
          node[minimum height=1cm, pattern=north west lines, draw, right=0 of pointer2] (sep3) {}
          node[minimum height=1cm, pattern=north west lines, draw, left=0 of pointer3] (sep4) {}
          node[draw, inner sep=0, behind path,
              fit=(pointer1)(pointer2)(pointer3)
                  (sep1)(sep2)(sep3)(sep4)
          ] (root) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root] (key11) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key11] (key21) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key11] (key31) {}
          node[minimum height=0.5cm, draw, below=0 of key11] (val11) {}
          node[minimum height=0.5cm, draw, left=0 of val11] (val21) {}
          node[minimum height=0.5cm, draw, right=0 of val11] (val31) {}
          node[draw, inner sep=0, behind path,
              fit=(key11)(key21)(key31)
                  (val11)(val21)(val31)
          ] (child1) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root.south west, xshift=-2cm] (key12) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key12] (key22) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key12] (key32) {}
          node[minimum height=0.5cm, draw, below=0 of key12] (val12) {}
          node[minimum height=0.5cm, draw, left=0 of val12] (val22) {}
          node[minimum height=0.5cm, draw, right=0 of val12] (val32) {}
          node[draw, inner sep=0, behind path,
              fit=(key12)(key22)(key32)
                  (val12)(val22)(val32)
          ] (child2) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root.south east, xshift=2cm] (key13) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key13] (key23) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key13] (key33) {}
          node[minimum height=0.5cm, draw, below=0 of key13] (val13) {}
          node[minimum height=0.5cm, draw, left=0 of val13] (val23) {}
          node[minimum height=0.5cm, draw, right=0 of val13] (val33) {}
          node[draw, inner sep=0, behind path,
              fit=(key13)(key23)(key33)
                  (val13)(val23)(val33)
          ] (child3) {};

        \draw[->] (pointer1.south) -- (key11.north);
        \draw[->] (pointer2.south) .. controls ([yshift=-1cm] pointer2) and ([yshift=1cm] key13) .. (key13.north);
        \draw[->] (pointer3.south) .. controls ([yshift=-1cm] pointer3) and ([yshift=1cm] key12) .. (key12.north);
    \end{tikzpicture}

@@
